An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-02-25 tex/paper.tex
Changing a paragraph and adding missing word
See
https://github.com/Axelrod-Python/An-open-reproducible-framework-for-the-study-of-the-iterated-prisoners-dilemma/issues/16

As mentioned before, IPD tournaments have been studied in an evolutionary
context: \cite{Ellison1994, Lee2015, Press2012, Stewart2012} consider this in a
traditional evolutionary game theory context. These works investigate
particular evolutionary contexts within which cooperation can emerge as stable.
Often these works consider direct opposition to another strategy and disregard
the population dynamics, for example in \cite{Lee2015} a machine learning
algorithm outperforms a strategy found in \cite{Press2012}.

@@

Due to the open nature of the library the number of strategies included has
grown at a fast pace, as can be seen in
Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
previous research being done in an irreproducible, with for example no
source code, and/or vaguely described strategies, not all previous tournaments
are yet to be reproduced. In fact, some of the early tournaments might be
impossible to reproduce as the source code is forever lost, this library aims to
prevent this from happening again in the future.

>>>>

As mentioned before, IPD tournaments have been studied in an evolutionary
context: \cite{Ellison1994, Lee2015, Press2012, Stewart2012} consider this in a
traditional evolutionary game theory context. These works investigate
particular evolutionary contexts within which cooperation can evolve and
persist. This can be in the context of direct interactions between strategies
or population dynamics for populations of many players using a variety of
strategies, which can lead to very different results. For example, in
\cite{Lee2015} a machine learning algorithm in a population context outperforms
strategies described in \cite{Press2012} and \cite{Stewart2012} that are
claimed to dominate any evolutionary opponent in head-to-head interactions.

@@

Due to the open nature of the library the number of strategies included has
grown at a fast pace, as can be seen in
Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
previous research being done in an irreproducible manner, with for example no
source code, and/or vaguely described strategies, not all previous tournaments
are yet to be reproduced. In fact, some of the early tournaments might be
impossible to reproduce as the source code is forever lost, this library aims
to prevent this from happening again in the future.
